---
title: "Noticias_2"
author: "Andrea García Tapia"
date: "2 de julio de 2015"
output: html_document
---
```{r, echo=FALSE, message=FALSE, warning=TRUE}
options(digits=2)
library(plyr)
library(dplyr)
library(knitr)
library(Hmisc)
library(ggplot2)
library(lubridate)
library(tidyr)
library(stringr)
library(reshape2)
library(igraph)

```

#DataBase description

The period of study we selected is 2 days before tropical storm Ingrid begin and 15 days after tropical storm Mauel ended. Since Eficiencia Informativa platform does not allowed to download all the news in a period we started with a small sample of the news related to "Ingrid"  *AND* "Manuel" for the period 09/09/13-10/02/13. 

```{r}
IM <- read.csv("~/Dropbox/Tesis_CD/Datos/Noticias/I&M/IM.csv", stringsAsFactors=FALSE)
#hay un problema
describe(IM[5]) # en la variable 5 (Tipo de Medio) 
describe(IM[8])#Titulo
describe(IM[9])
describe(IM[10])
describe(IM[12])
unique(IM[5])
#no hay problema 
describe(IM[1:4])
describe(IM[6:7])
describe(IM[11])
describe(IM[13:18])

names(IM)
head(IM)
```
Nos quedamos con solo el resumen tinformativo para poder extraer los temas 
```{r}
noticias <- IM[9]
save(noticias, file='~/Dropbox/Tesis_CD/Limpieza/noticias.Rdata')
